Tensor denoising and completion based on ordinal observations

### 2020-03-05 paper/arxiv/correction.tex
upload correction.tex

Therefore, there exists a positive constant $c_1>0$ (? perhaps depending on $\alpha, \beta,\Delta$ etc...needs some calculation..) such that
\[
\max_{\mz\in\tS,\mz\neq \mathbf{0}}{\sum_{\omega,\ell} z^2_{\omega,\ell}\mathds{1}_{\{y_\omega=\ell \text{ or }\ell+1\}} \over \FnormSize{}{\mz}^2}\geq c_1 {\min_{\ell}(n_\ell+n_{\ell+1})\over (L-1)\prod_k d_k}\geq c_1 {\min_{\ell}(n_\ell+n_{\ell+1})\over (L-1)\prod_k d_k}. 
\]
The conclusion~\eqref{eq:clt} then follows by applying the law of large number and the uniform bound $\min_{z_{\omega,\ell}}\mathbb{P}(y_{\omega}=\ell \text{ or }\ell+1|z_{\omega,\ell})\geq 2A_{\alpha,\beta,\Delta}$ to the ratio:
\[
{\min_{\ell}(n_\ell+n_{\ell+1})\over \prod_k d_k}\geq 2A_{\alpha,\beta,\Delta}, \quad \text{ in high probability as $d_{\min}\to \infty$}.
\] 
}
\end{enumerate}1
\end{proof}
\bibliography{tensor_wang}
\bibliographystyle{apalike}
\end{document}

>>>>

Therefore, there exists a positive constant $c_1>0$ (? perhaps depending on $\alpha, \beta,\Delta$ etc...needs some calculation..) such that
\[
\max_{\mz\in\tS,\mz\neq \mathbf{0}}{\sum_{\omega,\ell} z^2_{\omega,\ell}\mathds{1}_{\{y_\omega=\ell \text{ or }\ell+1\}} \over \FnormSize{}{\mz}^2}\geq c_1 {\min_{\ell}(n_\ell+n_{\ell+1})\over (L-1)\prod_k d_k}\geq c_1 {\min_{\ell}(n_\ell+n_{\ell+1})\over (L-1)\prod_k d_k}. 
\]
The conclusion~\eqref{eq:clt} then follows by applying the law of large numbers and the uniform bound $\min_{z_{\omega,\ell}}\mathbb{P}(y_{\omega}=\ell \text{ or }\ell+1|z_{\omega,\ell})\geq 2A_{\alpha,\beta,\Delta}$ to the ratio:
\[
{\min_{\ell}(n_\ell+n_{\ell+1})\over \prod_k d_k}\geq 2A_{\alpha,\beta,\Delta}, \quad \text{ in high probability as $d_{\min}\to \infty$}.
\] 
}
\end{enumerate}1
\end{proof}
\bibliography{tensor_wang}
\bibliographystyle{apalike}
\end{document}
